Size-differentiated Export in Different Dynamical Regimes in the Ocean

### 2020-01-02 Submission_and_reviews/response_to_reviewers.tex

Additionally, the base of the euphotic zone is preferred in our study for three main reasons: 
			\begin{enumerate}
				\item A series of non-trivia important transformations occur in the euphotic zone \citep[e.g., grazing, material packaging, and many others; see][for example]{Denman_1999} that are not captured in our idealized setup, and are far beyond the scope of our study. By seeding particles at the base of the euphotic layer, we focus on the particulate material available to export, where remineralization and sinking are the dominant processes driving vertical fluxes (other than possibly advection, as demonstrated in this study). 
				\item The main results are expressed in terms of vertical fluxes. Vertical fluxes of particulate matter within the ML are not necessarily relevant to particle export, for the reasons detailed above. Including fluxes in the ML would introduce a bias into our results that is not relevant to our objectives.
				\item Seeding over 80 m instead of 10 m would require 8 times as many particles, as it is important to preserve particle density to adequately capture the physical dynamics at small scale (i.e., if particle seeding is too sparse, the presence of submesoscale dynamics would have little impact as no particles would be advected through these features). This would bring the total amount of particles tracked from $\sim$6 millions to $\sim$48 millions, largely limiting the number of experiments we could conduct in a reasonable time frame.
			\end{enumerate}

Finally, the small particles released at the base of the euphotic layer do not aim to represent small particles at the time of particle production. It can also represent larger particles at production that went through remineralization in the ML.

Based on this comment, the text has been modified in Section 2.2.2 to better justify the choices outlined above.\\

\subsection*{Major point \#2}
\textit{Second, it is unclear why 5m/day is selected for the largest particle class. Studies using Underwater Vision Profilers reveal that a large portion of the particle flux is contributed by large aggregates of 0.1-5mm, which can have sinking speeds above 100m/day (see Guidi et al. 2008, Kiko et al. 2017). Comparing the summer and winter simulations, it seems that small particles only dominate the export flux when vertical advective velocities exceed the large particle sinking velocity. This condition would not be met if an aggregate particle class with sinking velocity of 100m/day were included. I suggest the inclusion of an additional "large aggregate" size class with appropriate sinking speed.\\}

\textit{``it is unclear why 5m/day is selected for the largest particle class."\\}
The choice of 5m/day sinking rates as the ``face-sinking"  class is justified on lines 300-301 of the original manuscript. It is based on the PDFs of the advective vertical velocity. In our case, 5 m/day is faster than 85-90\% of the vertical velocity modeled in our domain at any given time. We have added some text in Section 2.2.2 to make the justification clearer to the reader.\\

\textit{``Comparing the summer and winter simulations, it seems that small particles only dominate the export flux when vertical advective velocities exceed the large particle sinking velocity."\\}
This is therefore not exact in this case. As mentioned, at any given time, between 10 and 15\% of the vertical velocity over the model domain is smaller than 5 m/day -- our fastest sinking rate -- and an even smaller percentage is sampled by the Lagrangian particles. If \textit{``vertical advective velocities exceed the large particle sinking velocity"}, it would be temporary and very rare.\\

However, your comment is very relevant: What do our findings mean for sinking rates far exceeding the maximum modeled vertical velocities? In that case, $w \approx w_s$, as the sinking rate largely dominate. We want to know if the ratio of fluxes of two large sinking velocity is greater and smaller than one (i.e., the slope of the biomass flux spectrum is positive or negative):

@@

\begin{equation}
	\frac{B_2w_2}{B_1w_1} >1 \quad \text{with} \quad w_2 > w_1
\end{equation}

Using Equation 8 in the main text, we obtain:
\begin{align}
	\frac{B_0\left(\frac{w_1}{w_0}\right)^{\frac{3-\xi}{2}}w_1}{B_0\left(\frac{w_2}{w_0}\right)^{\frac{3-\xi}{2}}w_2} &> 1\\[.2cm]
	\left(\frac{w_2}{w_1}\right)^{\frac{5-\xi}{2}} &>1
\end{align}	
which is only true for $w_2 > w_1$ if $\xi<$5. In other words, if the Junge slope is larger than 5, the slope of the particle size, biomass, AND biomass flux is negative. While large, a value of $\xi>5$ is not unrealistic, as it falls within the range of $\xi$ obtained from satellite-based estimates \citep{Kostadinov_2009}.

To directly address your comment, it is true that for very large aggregates with sinking rates far exceeding the order of magnitude of vertical velocities, the contribution of slower sinking particles is not dominant. We believe it to be well-established, and is the basis of the traditional 1-D model commonly used. Our study demonstrates the limitations of this paradigm, as one considers slower-sinking particles classes. Furthermore, for the largest aggregate to constantly be driving the biomass flux, it would require an infinite reservoir of those large particles to be able to relate their larger flux to larger export. The biomass flux due to the aggregates would be larger until the source is exhausted -- which is likely to happen more quickly for 100 m/day particles than for smaller particles. In fact, export from very fast sinking particles (e.g., 100 m /day) tend to occur as events \citep{Kiko_2017}.
Additionally, this paradigm is only true if the slope of the particle-size spectrum is smaller than $\sim$5 (based on our scaling).

Including a ``large aggregate" size class sinking at 100m/day, for example, would not provide much more interesting information, in our opinion. In fact, the flux of such a size class can be computed theoretically (using $w \approx w_s$) and does not require any model simulations. We agree, however, that this is an important fact to consider. As a result, we have added a paragraph in section 4.2 to put our findings in perspective with aggregates sinking at much faster sinking rates.

\subsection*{Major point \#3}
 \textit{Finally, the analysis demonstrated in Figures 7 and 8 does not seem appropriate for gauging the contribution of small and large particles to export, and the role of remineralization. As far as I understand, the insets in these figures show the flux associated with each particle class at 25 days after the particle release, computed based on their abundance and velocity (advective plus sinking).\\}

### 2020-01-02 size_differentiated_export.tex
Addressing more reviews

	%% ------------------------------------------------------------------------ %%
	%
	%  BEGIN ARTICLE
	%
	%% ------------------------------------------------------------------------ %%

	\section{Introduction}

@@

	In each particle-tracking experiment, four different classes of particles are released. Each particle class is characterized by a different sinking velocity: 0.025, \remove{0.05, }1, and 5 m/day. The slowest-sinking class is essentially selected to represent non-sinking particles: based on the setup of our experiments, the slowest-sinking particles would take 800 days on average to be exported to a depth of 100 m through gravitational sinking, a timescale much greater than commonly observed remineralization timescales. The fastest-sinking velocity is chosen as an end-member velocity class of particle that will be exported in its entirety over the course of our experiment. %The results presented for the 5 m/day sinking class can therefore be extrapolated to any class with a higher sinking velocity.

@@

	In the absence of remineralization, both a steeper size spectrum slope ($\xi>3$ in this case) and enhanced submesoscale dynamics, increase the contribution of slower-sinking particle classes to the downward biomass flux. 
	This is only when both of these conditions are combined, however, that slower-sinking particles dominate the downward flux of biomass (Figure \ref{fig: biomass_export}). 
	This is a significant result, as Junge slopes greater than 3 have been observed in the ocean \add{: In-situ observations yield average spectral slopes varying between 3.5 and 4.5 }\citep[see Table 2 in ]{Kostadinov_2009}\add{, while spectral analysis of satellite data suggest global spectral slopes varying between 3 and 6. More recent observational work located in the Northeast Pacific, including Station Papa, found a spectral slope also greater than 3}\citep[][; Z. Xiaodong, personal communication]{White_2015}.
    \add{Junge slopes are expected to vary in space, depending on the community composition, both lateraly and vertically} \citep{Kostadinov_2009, White_2015}\add{, as well as in time; spectrum slopes tend to be flatter during a spring bloom event, where larger particles (e.g., diatoms) are produced in large quantities (cite cite cite), and steeper during the wintertime, when communities are mostly composed of small particles (cite cite cite)}.
    The threshold value of $\xi =3$ for a change in the biomass spectral slope (see Figure \ref{fig: sinking_velocity_spectrum}b) is of course a consequence of first-order approximations used in this study describing the relationships between particle size, sinking velocity, and biomass content. Nevertheless, our results demonstrate the importance of including the smaller particle size range of the particle spectrum,  in the estimation or measurement of vertical fluxes, especially when submesoscale dynamics are active. It also highlights the importance of better constraining the relationships linking particle size, sinking velocity, and biomass content.

@@

>>>>

	%% ------------------------------------------------------------------------ %%
	%
	%  BEGIN ARTICLE
	%
	%% ------------------------------------------------------------------------ %%
	\section{Introduction}

@@

	In each particle-tracking experiment, four different classes of particles are released. Each particle class is characterized by a different sinking velocity: 0.025, \remove{0.05, }1, and 5 m/day. The slowest-sinking class is essentially selected to represent non-sinking particles: based on the setup of our experiments, the slowest-sinking particles would take 800 days on average to be exported to a depth of 100 m through gravitational sinking, a timescale much greater than commonly observed remineralization timescales. The fastest-sinking velocity is chosen as an end-member velocity class of particle\change{ that will be exported in its entirety over the course of our experiment. }{, based on the PDF of vertical velocities in the model. At any given time, at least 85\% of the model vertical velocity is weaker than 5 m/day. The results presented for the 5 m/day sinking class can therefore be theoretically extrapolated to any class with a higher sinking velocity.}

@@

	In the absence of remineralization, both a steeper size spectrum slope ($\xi>3$ in this case) and enhanced submesoscale dynamics, increase the contribution of slower-sinking particle classes to the downward biomass flux. 
	This is only when both of these conditions are combined, however, that slower-sinking particles dominate the downward flux of biomass (Figure \ref{fig: biomass_export}). 
	This is a significant result, as Junge slopes greater than 3 have been observed in the ocean \add{: In-situ observations yield average spectral slopes varying between 3.5 and 4.5 }\citep[see Table 2 in ]{Kostadinov_2009}\add{, while spectral analysis of satellite data suggest global spectral slopes varying between 3 and 6. More recent observational work located in the Northeast Pacific, including Station Papa, found a spectral slope also greater than 3}\citep[][; Z. Xiaodong, personal communication]{White_2015}.
    \add{Junge slopes are expected to vary in space, depending on the community composition, both lateraly and vertically} \citep{Kostadinov_2009, White_2015}\add{, as well as in time; spectrum slopes tend to be flatter during a spring bloom event, where larger particles (e.g., diatoms) are produced in large quantities, and steeper during the wintertime, when communities are mostly composed of small particles}.
    The threshold value of $\xi =3$ for a change in the biomass spectral slope (see Figure \ref{fig: sinking_velocity_spectrum}b) is of course a consequence of first-order approximations used in this study describing the relationships between particle size, sinking velocity, and biomass content. Nevertheless, our results demonstrate the importance of including the smaller particle size range of the particle spectrum,  in the estimation or measurement of vertical fluxes, especially when submesoscale dynamics are active. It also highlights the importance of better constraining the relationships linking particle size, sinking velocity, and biomass content.

@@

	\add{These results are robust to the range of sinking rates explored. If one considers a particle class with a sinking rate far exceeding the vertical advective velocity }\citep[e.g., 100 m/day; ][]{Turner_2015}\add{, then the associated biomass flux can be estimated by relying on the traditional 1-D paradigm, assuming $w_{tot}\approx w_s$. Combining this approximation with Equation \ref{eq: biomassjungeslope} shows that the slope of the biomass flux spectrum is positive for $\xi<5$, in which case very fast-sinking particles would dominate  vertical biomass fluxes. However, for $\xi>5$, the slope of the biomass flux spectrum become negative as well, meaning that the biomass flux is always dominated by the slow-sinking particle classes, regardless of the ocean dynamical regime. While considered large, values of $\xi > 5$ remain realistic and fall within the range obtained from satellite-based estimates} \citep{Kostadinov_2009}.
